Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-09 paper/paper.tex
Update NYTimes+ GloVe + LSTM results

\begin{figure}[t]
   \begin{center}
      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
   \end{center}
      \caption{Our transformer model attends over embeddings from three
      different domains (image patches, faces, and article text). Using
      byte-pair encoding, the model can then directly produce a caption
      containing specific named entities without the use of templates.}
   \label{fig:long}
   \label{fig:onecol}
\end{figure}

@@

BPE offers an elegant solution to handle an open vocabulary. To date the only
image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
their data preprocessing step, they explicitly removed rare named entities from
the captions. Thus no study has been done yet to see how well BPE used in
transformers can generate rare names.

In addition to attending to image patches, some captioning models attend to
objects \cite{Wang2019Hierarchical} and concept terms
\cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
image itself. When attending to more than one modality, there are various
strategies on how to combine embeddings such as addition, concatenation, and
using multivariate residual modules \cite{Wang2019Hierarchical}.

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning \cite{Biten2019GoodNews}. As part of the
quality check, we also reconstruct the same dataset on our own. We use the New
York Times API and write a custom parser to recollect and extract all the
articles and images in the same period as GoodNews from the original source. We
call this GoodNews+. We were able to crawl all the original articles, but the
number of images is slightly less, either due to dead links or not crawling
images unrelated to the main article. GoodNews+ allows us to make the following
observations about the original GoodNews dataset:

@@

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
      Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
      Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
      \midrule
      GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
      GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
      RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
      Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
      Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      GloVe + LSTM  & 15.3 & 12.3 \\
      GloVe + Transformer  & 15.1 & 12.9 \\
      RoBERTa + LSTM  & 15.6 & 13.4 \\
      Transformer (first 512 tokens)  & 15.3 & 13.6 \\
      Transformer (location-aware) & 15.1 & 13.5  \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\begin{figure}[t]
   \begin{center}
      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
   \end{center}
      \caption{Our transformer model attends to embeddings from three different
      domains (image patches, faces, and article text). Using byte-pair
      encoding, the model can then directly produce a caption containing
      specific named entities without the use of templates.}
   \label{fig:long}
   \label{fig:onecol}
\end{figure}

@@

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
their data preprocessing step, they explicitly removed rare named entities from
the captions. We attempt to fill this gap and in particular examine how much
better BPE can generate rare names compared to template-based methods.

In addition to attending to image patches, some captioning models also attend
to objects \cite{Wang2019Hierarchical} and concept terms
\cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
image itself. When attending to more than one modality, there are various
strategies on how to combine embeddings such as addition, concatenation, and
using multivariate residual modules \cite{Wang2019Hierarchical}.

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning \cite{Biten2019GoodNews}. As part of the
quality check, we also reconstruct the same dataset on our own. We use the New
York Times
API\footnote{\href{https://developer.nytimes.com/apis}{https://developer.nytimes.com/apis}}
and write a custom parser to recollect and extract all the articles and images
in the same period as GoodNews from the original source. We call this
GoodNews+. We were able to crawl all the original articles, but the number of
images is slightly less, either due to dead links or not crawling images
unrelated to the main article. GoodNews+ allows us to make the following
observations about the original GoodNews dataset:

@@

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
      GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
      Transformer (first 512 tokens) & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
      Transformer (location-aware) & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
      \midrule
      GloVe + LSTM & 12.4\% & 15.6\% & 0\% & 0\% & 0\% & 0\%  \\
      GloVe + Transformer & 18.3\% & 21.7\% & 0\% & 0\% & 0\% & 0\%  \\
      RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
      Transformer (first 512 tokens) & 30.3\% & 32.2\% & 22.6\% & 29.1\% & 20.1\% & 21.3\%  \\
      Transformer (location-aware) & 33.8\% & 36.5\% & 26.2\% & 32.5\% & 24.0\% & 25.6\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      GloVe + LSTM  & 13.8 & 11.8 \\
      GloVe + Transformer  & 15.1 & 12.9 \\
      RoBERTa + LSTM  & 15.6 & 13.4 \\
      Transformer (first 512 tokens)  & 15.3 & 13.6 \\
      Transformer (location-aware) & 15.1 & 13.5  \\
		\bottomrule
	\end{tabular}
\end{table*}
